---
title: "GeoPov Data and Methods"
# date: 2025-02-20
# date-format: long
# author: John Doe
---

:::::::::::: grid
::: {.g-col-lg-2 .g-col-md-1 .g-col-sm-0 .g-col-0}
:::

::::::::: {.g-col-lg-8 .g-col-md-10 .g-col-sm-12 .g-col-12}
::: lead
A curated list of spatial data sources & methods + applications to distributional analysis by [Geospatial Poverty Solutions](http://geopov/)

[UNDER CONSTRUCTION]{style="color: red;"}
:::

## Data

Quickly find, assess and learn how to access useful spatial indicators & data sources

<!-- Load functions and data -->

```{r include=FALSE}

# Function for creating drop down tables
source("code/dropdown_links.R")

# data catalog
data_list <- read.csv("data/data_list.csv")

# methods catalog
methods_list <- read.csv("methods/methods_list.csv")

```

```{r}
#| echo: false
#| eval: false
# This chunk's sole purpose is to trigger Quarto's dependency detection
library(leaflet)
```

<!-- Create drop down tables with data by theme -->

```{r echo=FALSE, results='asis'}
library(htmltools)

div(class = "blocks-container dropdown_list",
  class = "dropdown_list",
  list(
    dropdown_links(
      output_dir = "data",
      title = "People",
      link_data = data_list[grepl("People", data_list$theme), 2, drop = FALSE],
      outline_color = "#3498db",
      icon_path = "https://cdn-icons-png.flaticon.com/512/4807/4807598.png"
    ),

    dropdown_links(
      output_dir = "data",
      title = "Planet",
      link_data = data_list[grepl("Planet", data_list$theme), 2, drop = FALSE],
      outline_color = "#2ecc71",
      icon_path = "https://cdn-icons-png.flaticon.com/512/9985/9985721.png"
    ),

    dropdown_links(
      output_dir = "data",
      title = "Prosperity",
      link_data = data_list[grepl("Prosperity", data_list$theme), 2, drop = FALSE],
      outline_color = "#e74c3c",
      icon_path = "https://cdn-icons-png.flaticon.com/512/10074/10074713.png"
    ),

    dropdown_links(
      output_dir = "data",
      title = "Infrastructure",
      link_data = data_list[grepl("Infrastructure", data_list$theme), 2, drop = FALSE],
      outline_color = "#9b59b6",
      icon_path = "https://cdn-icons-png.flaticon.com/512/10074/10074713.png"
    ),

    dropdown_links(
      output_dir = "data",
      title = "Digital",
      link_data = data_list[grepl("Digital", data_list$theme), 2, drop = FALSE],
      outline_color = "#f39c12",
      icon_path = "https://cdn-icons-png.flaticon.com/512/10074/10074713.png"
    ),

    dropdown_links(
      output_dir = "data",
      title = "Boundaries",
      link_data = data_list[grepl("Boundaries", data_list$theme), 2, drop = FALSE],
      outline_color = "grey",
      icon_path = "https://cdn-icons-png.flaticon.com/512/10074/10074713.png"
    )
  )
)

```

::: {.callout-note collapse="true" appearance="minimal"}
### Data catalog

```{r}
#| echo: false
#| results: 'asis'
library(DT)
data_list <- read.csv("data/data_list.csv")

DT::datatable(
  data_list,
  escape = FALSE, # Allow HTML in table cells
  options = list(pageLength = 10),
  filter = 'top',
  class = 'cell-border stripe'
)

```
:::

#### Geocoded GMD

Harmonized household survey microdata with location information and spatial variables

::: {.callout-note collapse="true" appearance="minimal"}
### List of geocoded GMD surveys

-   Stata and R code to access, analyze and use the GMD data are provided under methods.

|             |          |                 |                   |                    |
|-------------|----------|-----------------|-------------------|--------------------|
| **Country** | **Year** | **Survey name** | **Location type** | **Location level** |
|             |          |                 |                   |                    |
:::

#### Space2Stats

[Space2Stats](https://worldbank.github.io/DECAT_Space2Stats) provide regularly requested geospatial aggregates at two scales:

-   Official World Bank boundaries at admin level 2
-   H3 hexagons at level 6 (\~36km2)

::: {.callout-note collapse="true" appearance="minimal"}
### S2S catalog

-   R and Python code to access the S2S data are provided on the [Space2Stats](https://worldbank.github.io/DECAT_Space2Stats/readme.html#api) site.

|           |               |
|-----------|---------------|
| **Theme** | **Name**      |
| People    | Population    |
| People    | Urbanization  |
| Climate   | Heat and Cold |
:::

## Methods and code

Methods and reproducible code to help you use spatial data for distributional analysis

```{r echo=FALSE, results='asis'}
methods_list <- read.csv("methods/methods_list.csv")

div(class = "blocks-container dropdown_list",
  class = "dropdown_list",
  list(
    dropdown_links(
      output_dir = "methods", 
      title = "Aggregate", 
      link_data = methods_list[grepl("Aggregate", methods_list$type), 2, drop = FALSE], 
      outline_color = "#3498db", 
      icon_path = "https://cdn-icons-png.flaticon.com/512/9308/9308941.png"
    ),
    
    dropdown_links(
      output_dir = "methods", 
      title = "Merge", 
      link_data = methods_list[grepl("Merge", methods_list$type), 2, drop = FALSE], 
      outline_color = "#f39c12", 
      icon_path = "https://cdn-icons-png.flaticon.com/512/9850/9850778.png"
    ),
    
    dropdown_links(
      output_dir = "methods", 
      title = "Map", 
      link_data = methods_list[grepl("Map", methods_list$type), 2, drop = FALSE], 
      outline_color = "#9b59b6", 
      icon_path = "https://cdn-icons-png.flaticon.com/512/854/854878.png"
    )
  )
)
```

```{r echo=FALSE, results='asis'}
methods_list <- read.csv("methods/methods_list.csv")

div(class = "blocks-container dropdown_list",
  class = "dropdown_list",
  list(
    dropdown_links(
      output_dir = "methods", 
      title = "Analyze", 
      link_data = methods_list[grepl("Analyze", methods_list$type), 2, drop = FALSE], 
      outline_color = "#e74c3c", 
      icon_path = "https://cdn-icons-png.flaticon.com/512/9850/9850778.png"
    )
  )
)
```

::: {.callout-note collapse="true" appearance="minimal"}
### Methods catalog

```{r}
#| echo: false
#| results: 'asis'
library(DT)
methods_list <- read.csv("methods/methods_list.csv")

DT::datatable(
  methods_list,
  escape = FALSE, # Allow HTML in table cells
  options = list(pageLength = 10),
  filter = 'top',
  class = 'cell-border stripe'
)

```
:::

## Applications

A curated & searchable list of spatial welfare analysis studies

::: {.callout-note collapse="true" appearance="minimal"}
### Studies

```{r echo=FALSE, results='asis'}
library(DT)

applications <- data.frame(Title = c(""), Authors = c(""), Summary = c(""), Data = c(""), Method = c(""), Reproducibility = c(""))

DT::datatable(
  applications,
  escape = FALSE, # Allow HTML in table cells
  options = list(pageLength = 10),
  filter = 'top',
  class = 'cell-border stripe'
)

```
:::

## Contribute

To suggest data or methods [open an issue on Github](link) and fill out the template or [contact us](mailto:bbrunckhorst@worldbank.org?subject=GeoPov%20data%20and%20methods%20repository).
:::::::::

::: {.g-col-lg-1 .g-col-md-1 .g-col-sm-0 .g-col-0}
:::
::::::::::::

```{=html}
<div class="secondary-links">
  <div class="secondary-links-container">
      <div class="secondary-links-title">
      </div>
      <div class="grid">
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12">
          <ul>
            <li><a href="http://GeoPov/">Geospatial Poverty Solutions Home</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="https://pipmaps.worldbank.org/">Geospatial poverty portal</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="mailto:bbrunckhorst@worldbank.org?subject=GeoPov%20data%20and%20methods%20repository" target="_top">Contact us</a></li>
          </ul>
        </div>
      </div>
    </div>
</div>
```
