---
title: "Mapping interview locations with GMD data"
format: html
---

::::::: grid
::: {.g-col-lg-2 .g-col-md-1 .g-col-sm-0 .g-col-0}
:::

:::: {.g-col-lg-8 .g-col-md-10 .g-col-sm-12 .g-col-12}


**Name:** Mapping interview locations with GMD data

**Keywords:** gmd, geovariables, household survey, geocoding, maps

**Type:** Map

**Description:** The locations geocoded in GMD surveys can be mapped using the H3 module, which links households to a discrete global grid. Where possible, GPS coordinates are also made available in the LOC module, although these have been modified from the true  locations. The code below shows how to map the locations mapped in the GMD data.

<small>
**Usage:** NA

**Limitations:** NA

**Examples:** NA

**Input:** NA

**Ouput:** NA

</small>

**Reproducible code**

::: panel-tabset

## R
```{r}
#| echo: false
#| output: asis
if (file.exists("../code/NA")) {
  cat("```r
")
  try(cat(readLines("../code/NA"), sep = "
"))
  cat("```
")
} else {
  cat("No code
")
}
```

## Output
```{r}
#| echo: false
#| message: false
#| warning: false
if (file.exists("../code/NA")) {
  try(source("../code/NA"))
} else {
  print("None")
}
```


:::

**Last updated:** 10/16/25

::::

::: {.g-col-lg-1 .g-col-md-1 .g-col-sm-0 .g-col-0}
:::
:::::::

```{=html}
<div class="secondary-links">
  <div class="secondary-links-container">
      <div class="secondary-links-title">
      </div>
      <div class="grid">
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12">
          <ul>
            <li><a href="http://GeoPov/">Geospatial Poverty Solutions Home</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="https://pipmaps.worldbank.org/">Geospatial poverty portal</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="mailto:bbrunckhorst@worldbank.org?subject=GeoPov%20data%20and%20methods%20repository" target="_top">Contact us</a></li>
          </ul>
        </div>
      </div>
    </div>
</div>
```


