---
title: "Built up area"
format: html
---

::: {.grid}
::: {.g-col-6}

**Name:** Built up area

**Source:** [GHSL - Global Human Settlement Layer](https://doi.org/10.2905/9F06F36F-4B11-47EC-ABB0-4F8B7B1D72EA)

**Version:** 1

**Keywords:** buildings, land use

**Type:** Raster

**Description:** The spatial raster dataset depicts the distribution of built-up surfaces, expressed as number of square metres. The data report about the total built-up surface and the built-up surface allocated to dominant non-residential (NRES) uses. Data are spatial-temporal interpolated or extrapolated from 1975 to 2030 in 5 years intervals. For the temporal anchor point of 2018 the data is published at 10m as observed from the S2 image data.

**Units:** m^2

**Available in geocoded GMD?** No

**Available from Space2Stats?** No

:::
::: {.g-col-6}

**Map**

```{r}
#| include: false
map_path <- paste0("../code/", "NA",".R")
if (file.exists(map_path)){knitr::read_chunk(map_path)}
```

```{r}
#| label: NA
#| echo: false
#| message: false
#| warning: false
```
<small>
<small>
**Coordinate reference system:** World Mollweide (EPSG:54009) or WGS84 (EPSG:4326)

**Spatial coverage:** Global

**Spatial resolution:** 10 m, 100 m, 1 km, 3 arcsec or 30 arcsec

**Temporal coverage:** 1975-2030

**Temporal resolution:** 5-year intervals

**License:** CC BY 4.0

**Citation:** Pesaresi M., Politis P. (2023): GHS-BUILT-S R2023A - GHS built-up surface grid, derived from Sentinel2 composite and Landsat, multitemporal (1975-2030)European Commission, Joint Research Centre (JRC) PID: http://data.europa.eu/89h/9f06f36f-4b11-47ec-abb0-4f8b7b1d72ea, doi:10.2905/9F06F36F-4B11-47EC-ABB0-4F8B7B1D72EA
</small>
</small>

:::
:::

::::::: grid
::: {.g-col-lg-8 .g-col-lg-offset-2 .g-col-md-10 .g-col-md-offset-1 .g-col-sm-12 .g-col-12}


<small>
**Usage:** NA

**Limitations:** NA

**Examples:** NA

**Access:** GHS-BUILT-S data files are available for direct download [here](https://human-settlement.emergency.copernicus.eu/download.php?ds=bu). The gridded data (.tif format) can be downloaded as a single global file for either Residential (RES) or non residential (NRES) classification. It is also available  in smaller tiles covering a specific area - see the website. There is a separate file for each 5-year epoch, coordinate reference system and spatial resolution available. The code below downloads and opens the data using R.
</small>

::: panel-tabset

## R
```{r}
#| echo: false
#| output: asis
if (file.exists("../code/NA")) {
  cat("```r
")
  try(cat(readLines("../code/NA"), sep = "
"))
  cat("```
")
} else {
  cat("No code
")
}
```

## Output
```{r}
#| echo: false
#| results: hold
if (file.exists("../code/NA")) {
  try(source("../code/NA"))
} else {
  print("None")
}
```

:::

**Last updated:** 10/17/25

:::
:::::::

```{=html}
<div class="secondary-links">
  <div class="secondary-links-container">
      <div class="secondary-links-title">
      </div>
      <div class="grid">
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12">
          <ul>
            <li><a href="http://GeoPov/">Geospatial Poverty Solutions Home</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="https://pipmaps.worldbank.org/">Geospatial poverty portal</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="mailto:bbrunckhorst@worldbank.org?subject=GeoPov%20data%20and%20methods%20repository" target="_top">Contact us</a></li>
          </ul>
        </div>
      </div>
    </div>
</div>
```


