---
title: "Conflict events"
format: html
---

::: {.grid}
::: {.g-col-6}

**Name:** Conflict events

**Source:** [ACLED](https://acleddata.com/conflict-data)

**Version:** NA

**Keywords:** conflict, violence, fragility

**Type:** Vector

**Description:** ACLED collects the dates, actors, locations, fatalities, and types of all reported political violence and protest events in more than 200 countries and territories in real time.

**Units:** NA

**Available in geocoded GMD?** NA

**Available from Space2Stats?** NA

:::
::: {.g-col-6}

**Map**

```{r}
#| include: false
map_path <- paste0("../code/", "NA",".R")
if (file.exists(map_path)){knitr::read_chunk(map_path)}
```

```{r}
#| label: NA
#| echo: false
#| message: false
#| warning: false
```
<small>
<small>
**Coordinate reference system:** NA

**Spatial coverage:** Global

**Spatial resolution:** NA

**Temporal coverage:** NA

**Temporal resolution:** NA

**License:** NA

**Citation:** NA
</small>
</small>

:::
:::

::::::: grid
::: {.g-col-lg-8 .g-col-lg-offset-2 .g-col-md-10 .g-col-md-offset-1 .g-col-sm-12 .g-col-12}



<small>
**Usage:** NA

**Limitations:** NA

**Examples:** NA

**Access:** To dowload ACLED data, you must first [register an account](https://acleddata.com/myacled), then agree to the privacy policy, terms and conditions. Data files can then be downloaded from the website or using the dedicated R package [`acledR`](https://dtacled.github.io/acledR). The code below shows how to access and map ACLED indicators using R.
</small>

::: panel-tabset

## R
```{r}
#| echo: false
#| output: asis
if (file.exists("../code/NA")) {
  cat("```r
")
  try(cat(readLines("../code/NA"), sep = "
"))
  cat("```
")
} else {
  cat("No code
")
}
```

## Output
```{r}
#| echo: false
#| results: hold
if (file.exists("../code/NA")) {
  try(source("../code/NA"))
} else {
  print("None")
}
```

:::

**Last updated:** NA

:::
:::::::

```{=html}
<div class="secondary-links">
  <div class="secondary-links-container">
      <div class="secondary-links-title">
      </div>
      <div class="grid">
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12">
          <ul>
            <li><a href="http://GeoPov/">Geospatial Poverty Solutions Home</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="https://pipmaps.worldbank.org/">Geospatial poverty portal</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="mailto:bbrunckhorst@worldbank.org?subject=GeoPov%20data%20and%20methods%20repository" target="_top">Contact us</a></li>
          </ul>
        </div>
      </div>
    </div>
</div>
```


