---
title: "Degree of Urbanisation"
format: html
---

::: {.grid}
::: {.g-col-6}

**Name:** Degree of Urbanisation

**Source:** [GHSL - Global Human Settlement Layer](https://doi.org/10.2905/A0DF7A6F-49DE-46EA-9BDE-563437A6E2BA)

**Version:** GHS-SMOD - R2023A V2

**Keywords:** population, urbanization, rural, urban, cities

**Type:** Raster

**Description:** The dataset applies the Degree of Urbanisation stage I methodology recommended by UN Statistical Commission to the global population grid generated by the JRC in the epochs 1975-2030 (5 years timestep).
It is generated by integration of built-up surface extracted from Landsat and Sentinel-2 image data processing (GHS-BUILT-S R2023), and population data derived from the CIESIN GPW v4.11 (GHS-POP R2023). The data is provided at the detailed settlement model level (L2) with each 1 km grid cell assigned to one of 7 categories (or water). The first level (L1) can be obtained aggregating L2  to 3 categories: Urban centre, Urban cluster or Rural.

**Units:** Categorical: 10 = water, 11 = very low density rural, 12 = low density rural, 13 = rural cluster, 21 = suburban or peri-urban, 22 = semi-dense urban, 23 = dense urban, 30 = urban centre.

**Available in geocoded GMD?** Yes

**Available from Space2Stats?** Yes

:::
::: {.g-col-6}

**Map**

```{r}
#| include: false
map_path <- paste0("../code/", "NA",".R")
if (file.exists(map_path)){knitr::read_chunk(map_path)}
```

```{r}
#| label: NA
#| echo: false
#| message: false
#| warning: false
```
<small>
<small>
**Coordinate reference system:** World Mollweide (EPSG:54009)

**Spatial coverage:** Global

**Spatial resolution:** 1 km

**Temporal coverage:** 1975-2030

**Temporal resolution:** 5-year intervals

**License:** CC BY 4.0

**Citation:** Schiavina M., Melchiorri M., Pesaresi M. (2023):
GHS-SMOD R2023A - GHS settlement layers, application of the Degree of Urbanisation methodology (stage I) to GHS-POP R2023A and GHS-BUILT-S R2023A, multitemporal (1975-2030)European Commission, Joint Research Centre (JRC) PID: http://data.europa.eu/89h/a0df7a6f-49de-46ea-9bde-563437a6e2ba, doi:10.2905/A0DF7A6F-49DE-46EA-9BDE-563437A6E2BA

</small>
</small>

:::
:::

::::::: grid
::: {.g-col-lg-8 .g-col-lg-offset-2 .g-col-md-10 .g-col-md-offset-1 .g-col-sm-12 .g-col-12}


<small>
**Usage:** The Global Human Settlement Layer (GHSL) Degree of Urbanisation dataset can be used for international statistical comparison, urban planning, monitoring development goals, and spatial analysis. It classifies areas as cities, towns, or rural areas based on population density and size, making it useful for creating comparable urban statistics, analyzing access to services, and monitoring progress.

**Limitations:** NA

**Examples:** NA

**Access:** GHS-SMOD data files are available for direct download [here](https://human-settlement.emergency.copernicus.eu/download.php?ds=smod). The gridded degree of urbanisation data (.tif format) can be downloaded as a single global file or in smaller files covering a specific area as shown on the website. There is a separate file for each 5-year epoch. The code below downloads and opens the data using R.
</small>

::: panel-tabset

## R
```{r}
#| echo: false
#| output: asis
if (file.exists("../code/NA")) {
  cat("```r
")
  try(cat(readLines("../code/NA"), sep = "
"))
  cat("```
")
} else {
  cat("No code
")
}
```

## Output
```{r}
#| echo: false
#| results: hold
if (file.exists("../code/NA")) {
  try(source("../code/NA"))
} else {
  print("None")
}
```

:::

**Last updated:** 10/17/25

:::
:::::::

```{=html}
<div class="secondary-links">
  <div class="secondary-links-container">
      <div class="secondary-links-title">
      </div>
      <div class="grid">
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12">
          <ul>
            <li><a href="http://GeoPov/">Geospatial Poverty Solutions Home</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="https://pipmaps.worldbank.org/">Geospatial poverty portal</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="mailto:bbrunckhorst@worldbank.org?subject=GeoPov%20data%20and%20methods%20repository" target="_top">Contact us</a></li>
          </ul>
        </div>
      </div>
    </div>
</div>
```


