---
title: "Electricity access and reliability"
format: html
---

::: {.grid}
::: {.g-col-6}

**Name:** Electricity access and reliability

**Source:** [HREA](https://hrea.isr.umich.edu)

**Version:** 1.1000000000000001

**Keywords:** energy, power, night lights

**Type:** Raster

**Description:** High Resolution Electricity Access (HREA) indicator data are derived from statistical processing of nightly satellite observations of the earth at night. HREA provides 4 variables measuring electricity access and reliability: Mean annual natural logged visible radiance (in nW/cm2/sr), Mean z-score (standardized residuals), Light score (transformation of mean z-score), Proportion of nights a settlement is brighter than uninhabited areas.

**Units:** NA

**Available in geocoded GMD?** NA

**Available from Space2Stats?** NA

:::
::: {.g-col-6}

**Map**

```{r}
#| include: false
map_path <- paste0("../code/", "NA",".R")
if (file.exists(map_path)){knitr::read_chunk(map_path)}
```

```{r}
#| label: NA
#| echo: false
#| message: false
#| warning: false
```
<small>
<small>
**Coordinate reference system:** WGS84 (EPSG:4326)

**Spatial coverage:** 115 countries not fully electrified (2015)

**Spatial resolution:** 1 arc second, 7.5 arc second

**Temporal coverage:** 2013-2020

**Temporal resolution:** annual

**License:** CC BY 4.0

**Citation:** Brian Min, Zachary P. O'Keeffe, Babatunde Abidoye, Kwawu Mensan Gaba, Trevor Monroe, Benjamin P. Stewart, Kim Baugh, Bruno Sánchez-Andrade Nuño, “Lost in the Dark: A Survey of Energy Poverty from Space,” Joule (2024), https://doi.org/10.1016/j.joule.2024.05.001.
</small>
</small>

:::
:::

::::::: grid
::: {.g-col-lg-8 .g-col-lg-offset-2 .g-col-md-10 .g-col-md-offset-1 .g-col-sm-12 .g-col-12}



<small>
**Usage:** NA

**Limitations:** while they are calculated at the 15 arcsec level, they are provided at the higher resolution of the original settlement layer to represent the settlement distribution.

**Examples:** NA

**Access:** NA
</small>

::: panel-tabset

## R
```{r}
#| echo: false
#| output: asis
if (file.exists("../code/NA")) {
  cat("```r
")
  try(cat(readLines("../code/NA"), sep = "
"))
  cat("```
")
} else {
  cat("No code
")
}
```

## Output
```{r}
#| echo: false
#| results: hold
if (file.exists("../code/NA")) {
  try(source("../code/NA"))
} else {
  print("None")
}
```

:::

**Last updated:** 10/17/25

:::
:::::::

```{=html}
<div class="secondary-links">
  <div class="secondary-links-container">
      <div class="secondary-links-title">
      </div>
      <div class="grid">
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12">
          <ul>
            <li><a href="http://GeoPov/">Geospatial Poverty Solutions Home</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="https://pipmaps.worldbank.org/">Geospatial poverty portal</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="mailto:bbrunckhorst@worldbank.org?subject=GeoPov%20data%20and%20methods%20repository" target="_top">Contact us</a></li>
          </ul>
        </div>
      </div>
    </div>
</div>
```


