---
title: "International Wealth Index (IWI)"
format: html
---

::: {.grid}
::: {.g-col-6}

**Name:** International Wealth Index (IWI)

**Source:** [Lee & Braithwaite (2022)](https://doi.org/10.7910/DVN/5OGWYM)

**Version:** 1

**Keywords:** iwi, wealth index, poverty, assets, DHS

**Type:** Vector

**Description:** The dataset estimates the International Wealth Index which is a comparable asset based wealth index by utilizing publicly available geospatial data and machine learning methods. The method combines an XGBoost model and a convolutional neural network (CNN) model to estimate wealth index from both geospatial features and satellite images. Data-wise, training data was collected from 6 sources: OpenStreetMap (OSM), Demographic and Health Survey (DHS), UN OCHA settlements dataset (OCHA), Visible Infrared Imaging Radiometer Suite Nighttime Lights (VNL), Daytime satellite images through Google Static Maps API (Google Maps), High-Resolution Settlement Layer (HRSL) and the WorldPop gridded population dataset (WorldPop).

**Units:** NA

**Available in geocoded GMD?** NA

**Available from Space2Stats?** NA

:::
::: {.g-col-6}

**Map**

```{r}
#| include: false
map_path <- paste0("../code/", "NA",".R")
if (file.exists(map_path)){knitr::read_chunk(map_path)}
```

```{r}
#| label: NA
#| echo: false
#| message: false
#| warning: false
```
<small>
<small>
**Coordinate reference system:** NA

**Spatial coverage:** 929,295 populated places in 44 SSA countries

**Spatial resolution:** NA

**Temporal coverage:** NA

**Temporal resolution:** NA

**License:** CC0 1.0

**Citation:** Lee, K., & Braithwaite, J. (2022). High-resolution poverty maps in sub-saharan africa. World Development, 159, 106028.
Lee, Kamwoo, 2022, "High-resolution poverty maps in Sub-Saharan Africa", https://doi.org/10.7910/DVN/5OGWYM, Harvard Dataverse, V1, UNF:6:NY6/wSxRxmzx07Yq0S/DbQ== [fileUNF]
</small>
</small>

:::
:::

::::::: grid
::: {.g-col-lg-8 .g-col-lg-offset-2 .g-col-md-10 .g-col-md-offset-1 .g-col-sm-12 .g-col-12}


<small>
**Usage:** NA

**Limitations:** NA

**Examples:** NA

**Access:** NA
</small>

::: panel-tabset

## R
```{r}
#| echo: false
#| output: asis
if (file.exists("../code/NA")) {
  cat("```r
")
  try(cat(readLines("../code/NA"), sep = "
"))
  cat("```
")
} else {
  cat("No code
")
}
```

## Output
```{r}
#| echo: false
#| results: hold
if (file.exists("../code/NA")) {
  try(source("../code/NA"))
} else {
  print("None")
}
```

:::

**Last updated:** NA

:::
:::::::

```{=html}
<div class="secondary-links">
  <div class="secondary-links-container">
      <div class="secondary-links-title">
      </div>
      <div class="grid">
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12">
          <ul>
            <li><a href="http://GeoPov/">Geospatial Poverty Solutions Home</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="https://pipmaps.worldbank.org/">Geospatial poverty portal</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="mailto:bbrunckhorst@worldbank.org?subject=GeoPov%20data%20and%20methods%20repository" target="_top">Contact us</a></li>
          </ul>
        </div>
      </div>
    </div>
</div>
```


