---
title: "Nighttime lights"
format: html
---

::: {.grid}
::: {.g-col-6}

**Name:** Nighttime lights

**Source:** [NASA Black Marble](https://blackmarble.gsfc.nasa.gov/)

**Version:** 2

**Keywords:** nightlights, electricity, brightness, economic activity

**Type:** Raster

**Description:** NASA's Black Marble  nighttime lights datasets are derived from VIIRS, providing daily, monthly, and annual composites with advanced corrections for clouds, atmosphere, stray light, terrain, and lunar illumination. The data provide consistent, comparable brightness products.

**Units:** nW/cm^2/sr

**Available in geocoded GMD?** Yes

**Available from Space2Stats?** Yes

:::
::: {.g-col-6}

**Map**

```{r}
#| include: false
map_path <- paste0("../code/", "NA",".R")
if (file.exists(map_path)){knitr::read_chunk(map_path)}
```

```{r}
#| label: NA
#| echo: false
#| message: false
#| warning: false
```
<small>
<small>
**Coordinate reference system:** WGS84 (EPSG:4326)

**Spatial coverage:** Global

**Spatial resolution:** 15 arc-second (~500 m at the equator)

**Temporal coverage:** 2012-present

**Temporal resolution:** daily, monthly, annual

**License:** open data policy with no use restrictions

**Citation:** Román, M.O., Wang, Z., Sun, Q., Kalb, V., Miller, S.D., Molthan, A., Schultz, L., Bell, J., Stokes, E.C., Pandey, B. and Seto, K.C., et al. (2018). NASA's Black Marble nighttime lights product suite. Remote Sensing of Environment 210, 113-143. doi:10.1016/j.rse.2018.03.017.
</small>
</small>

:::
:::

::::::: grid
::: {.g-col-lg-8 .g-col-lg-offset-2 .g-col-md-10 .g-col-md-offset-1 .g-col-sm-12 .g-col-12}


<small>
**Usage:** Consistent, corrected brightness for tracking urbanization, disaster impacts, power outages, light pollution, and socio‑economic proxies—especially when methodological comparability across space/time is essential

**Limitations:** NA

**Examples:** NA

**Access:** BlackMarbleR is a R package developed at the World Bank that provides a simple way to use nighttime lights data from NASA’s Black Marble.
</small>

::: panel-tabset

## R
```{r}
#| echo: false
#| output: asis
if (file.exists("../code/NA")) {
  cat("```r
")
  try(cat(readLines("../code/NA"), sep = "
"))
  cat("```
")
} else {
  cat("No code
")
}
```

## Output
```{r}
#| echo: false
#| results: hold
if (file.exists("../code/NA")) {
  try(source("../code/NA"))
} else {
  print("None")
}
```

:::

**Last updated:** 10/17/25

:::
:::::::

```{=html}
<div class="secondary-links">
  <div class="secondary-links-container">
      <div class="secondary-links-title">
      </div>
      <div class="grid">
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12">
          <ul>
            <li><a href="http://GeoPov/">Geospatial Poverty Solutions Home</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="https://pipmaps.worldbank.org/">Geospatial poverty portal</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="mailto:bbrunckhorst@worldbank.org?subject=GeoPov%20data%20and%20methods%20repository" target="_top">Contact us</a></li>
          </ul>
        </div>
      </div>
    </div>
</div>
```


