---
title: "Travel time"
format: html
---

::: {.grid}
::: {.g-col-6}

**Name:** Travel time

**Source:** [Weiss et al. (2018), Weiss et al. (2020), Ryan et al. (2025)](https://doi.org/10.1038/nature25181, https://doi.org/10.1038/s41591-020-1059-1, https://idem-lab.github.io/traveltime/)

**Version:** software: 0.0.0.9000

**Keywords:** travel time, accessibility, cities

**Type:** Raster

**Description:** Travel time to nearest urban centre: Weiss et al. (2018) https://doi.org/10.1038/nature25181

Travel time to nearest health facility: Weiss et al. (2020)https://doi.org/10.1038/s41591-020-1059-1

Travel time to … anywhere. The R package [`traveltime`](https://idem-lab.github.io/traveltime/) enables a user to create a map of travel time over an area of interest from a user-specified set of geographic coordinates and friction surface. The package provides convenient access to global friction surfaces for walking and motorised travel for the year 2020. The final result is a raster of the area of interest where the value in each cell is the lowest travel time in minutes to any of the specified locations.

**Units:** minutes

**Available in geocoded GMD?** Yes

**Available from Space2Stats?** Yes

:::
::: {.g-col-6}

**Map**

```{r}
#| include: false
map_path <- paste0("../code/", "NA",".R")
if (file.exists(map_path)){knitr::read_chunk(map_path)}
```

```{r}
#| label: NA
#| echo: false
#| message: false
#| warning: false
```
<small>
<small>
**Coordinate reference system:** WGS84 (EPSG:4326) / defined by user inputs

**Spatial coverage:** Global /  defined by user inputs

**Spatial resolution:** 30 arcsec (~ 1km)  / defined by user inputs

**Temporal coverage:** 2020 friction surface / defined by user inputs

**Temporal resolution:** point in time of friction surface / defined by user inputs

**License:** travel time data: CC BY 4.0
software: MIT license

**Citation:** Ryan GE, Tierney N, Golding N and Weiss DJ. traveltime: an R package to calculate travel time across a landscape from user-specified locations. Gates Open Res 2025, 9:50 (https://doi.org/10.12688/gatesopenres.16356.1)
D. J. Weiss, A. Nelson, C. A. Vargas-Ruiz, K. Gligoric, S., Bavadekar, E. Gabrilovich, A. Bertozzi-Villa, J. Rozier, H. S. Gibson, T., Shekel, C. Kamath, A. Lieber, K. Schulman, Y. Shao, V. Qarkaxhija, A. K. Nandi, S. H. Keddie, S. Rumisha, P. Amratia, R. Arambepola, E. G. Chestnutt, J. J. Millar, T. L. Symons, E. Cameron, K. E. Battle, S. Bhatt, and P. W. Gething. Global maps of travel time to healthcare facilities. (2020) Nature Medicine. https://doi.org/10.1038/s41591-020-1059-1
</small>
</small>

:::
:::

::::::: grid
::: {.g-col-lg-8 .g-col-lg-offset-2 .g-col-md-10 .g-col-md-offset-1 .g-col-sm-12 .g-col-12}



<small>
**Usage:** The R package implements methods from Weiss et al. 2018, 2020 to calculate travel time from given locations over a friction surface. Pre-prepared walking or motorised friction surfaces can be obtained with `get_friction_surface`. User can also provide their own friction surface. This surface but must be in resistance units (1/conductance), e.g. minutes/meter. See Van Etten 2017.

**Limitations:** Over large areas this function can require significant RAM and will be slow.

**Examples:** NA

**Access:** Direct download travel time rasters from Malaria Atlas Project.R package: https://idem-lab.github.io/traveltime/
</small>

::: panel-tabset

## R
```{r}
#| echo: false
#| output: asis
if (file.exists("../code/NA")) {
  cat("```r
")
  try(cat(readLines("../code/NA"), sep = "
"))
  cat("```
")
} else {
  cat("No code
")
}
```

## Output
```{r}
#| echo: false
#| results: hold
if (file.exists("../code/NA")) {
  try(source("../code/NA"))
} else {
  print("None")
}
```

:::

**Last updated:** 10/17/25

:::
:::::::

```{=html}
<div class="secondary-links">
  <div class="secondary-links-container">
      <div class="secondary-links-title">
      </div>
      <div class="grid">
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12">
          <ul>
            <li><a href="http://GeoPov/">Geospatial Poverty Solutions Home</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="https://pipmaps.worldbank.org/">Geospatial poverty portal</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="mailto:bbrunckhorst@worldbank.org?subject=GeoPov%20data%20and%20methods%20repository" target="_top">Contact us</a></li>
          </ul>
        </div>
      </div>
    </div>
</div>
```


