---
title: "Urban centres"
format: html
---

::: {.grid}
::: {.g-col-6}

**Name:** Urban centres

**Source:** [GHSL - Global Human Settlement Layer](https://human-settlement.emergency.copernicus.eu/ghs_ucdb_2024.php)

**Version:** GHS-UCDB R2024A V1.1

**Keywords:** population, urbanization, rural, urban, cities

**Type:** Vector

**Description:** The GHS Urban Centre Database (GHS-UCDB) describes spatial entities called “Urban Centres” described through a set of multi-temporal thematic attributes from the GHSL data combined with other free and open data sets. The Urban Centres are defined by specific cut-off values on resident population and built-up surface share in a 1x1 km uniform global grid.

**Units:** NA

**Available in geocoded GMD?** No

**Available from Space2Stats?** No

:::
::: {.g-col-6}

**Map**

```{r}
#| include: false
map_path <- paste0("../code/", "NA",".R")
if (file.exists(map_path)){knitr::read_chunk(map_path)}
```

```{r}
#| label: NA
#| echo: false
#| message: false
#| warning: false
```
<small>
<small>
**Coordinate reference system:** World Mollweide, EPSG:54009

**Spatial coverage:** Global

**Spatial resolution:** 1 km

**Temporal coverage:** 1975-2030

**Temporal resolution:** 5-year intervals

**License:** CC BY 4.0

**Citation:** European Commission, Joint Research Centre, Melchiorri, M., Mari Rivero, I., Florio, P., Schiavina,
M., Krasnodebska, K., Politis, P., Uhl, J., Pesaresi, M., Maffenini, L., Sulis, P., Crippa, M., Guizzardi, D., Pisoni, E., Belis, C.,
Oom, D., Branco, A., Mwaniki, D., Githira, D., Kochulem, E., Tommasi, P., Carioli, A., Ehrlich, D., Kemper, T. and Dijkstra, L.,
Stats in the City – the GHSL Urban Centre Database 2025, Publications Office of the European Union, Luxembourg, 2024,
https://data.europa.eu/doi/10.2760/3046391, JRC139768.
</small>
</small>

:::
:::

::::::: grid
::: {.g-col-lg-8 .g-col-lg-offset-2 .g-col-md-10 .g-col-md-offset-1 .g-col-sm-12 .g-col-12}



<small>
**Usage:** The GHS Urban Centre Database (GHS-UCDB) can be used for urban planning, disaster risk reduction, transportation planning, and environmental monitoring by providing spatial and thematic data on cities globally. It helps identify urban extents and provides multi-dimensional attributes across various domains like geography, socio-economics, and sustainable development.

**Limitations:** NA

**Examples:** NA

**Access:** GHS-UCDB data files are available for direct download [here](https://human-settlement.emergency.copernicus.eu/download.php?ds=ucdb). The full urban centre data (.gpkg format) can be downloaded as a single global vector file or by theme and region. Tabular data is also available for download. The code below downloads and opens the data using R.
</small>

::: panel-tabset

## R
```{r}
#| echo: false
#| output: asis
if (file.exists("../code/NA")) {
  cat("```r
")
  try(cat(readLines("../code/NA"), sep = "
"))
  cat("```
")
} else {
  cat("No code
")
}
```

## Output
```{r}
#| echo: false
#| results: hold
if (file.exists("../code/NA")) {
  try(source("../code/NA"))
} else {
  print("None")
}
```

:::

**Last updated:** 10/17/25

:::
:::::::

```{=html}
<div class="secondary-links">
  <div class="secondary-links-container">
      <div class="secondary-links-title">
      </div>
      <div class="grid">
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12">
          <ul>
            <li><a href="http://GeoPov/">Geospatial Poverty Solutions Home</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="https://pipmaps.worldbank.org/">Geospatial poverty portal</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="mailto:bbrunckhorst@worldbank.org?subject=GeoPov%20data%20and%20methods%20repository" target="_top">Contact us</a></li>
          </ul>
        </div>
      </div>
    </div>
</div>
```


