---
title: "World Bank Official Boundaries"
format: html
---

::: {.grid}
::: {.g-col-6}

**Name:** World Bank Official Boundaries

**Source:** [World Bank](https://datacatalog.worldbank.org/search/dataset/0038272/World-Bank-Official-Boundaries)

**Version:** 5

**Keywords:** boundaries, regions, national, subnational, administrative, admin-1, admin-2

**Type:** Vector

**Description:** High resolution, World Bank-approved administrative boundaries. Each download option (shapefile, GeoPackage, or GeoJSON format) includes Admin 0, 1, 2, Non-Determined Legal Status Areas (NDLSA), and an ocean mask. An Admin 0 line file (for visualization purposes with World Bank-specific drawing instructions) can also be found in the shapefile folder. A data dictionary and additional columns of information which can be joined to the Admin 1 and 2 files are available as separate downloads.


**Units:** NA

**Available in geocoded GMD?** Yes

**Available from Space2Stats?** Yes

:::
::: {.g-col-6}

**Map**

```{r}
#| include: false
map_path <- paste0("../code/", "NA",".R")
if (file.exists(map_path)){knitr::read_chunk(map_path)}
```

```{r}
#| label: NA
#| echo: false
#| message: false
#| warning: false
```
<small>
<small>
**Coordinate reference system:** WGS84 (EPSG:4326)

**Spatial coverage:** Global

**Spatial resolution:** High resolution

**Temporal coverage:** 2025

**Temporal resolution:** 2025

**License:** CC-BY 4.0

**Citation:** World Bank. (2025). World Bank Official Boundaries. World Bank. https://datacatalog.worldbank.org/search/dataset/0038272/World-Bank-Official-Boundaries?version=5
</small>
</small>

:::
:::

::::::: grid
::: {.g-col-lg-8 .g-col-lg-offset-2 .g-col-md-10 .g-col-md-offset-1 .g-col-sm-12 .g-col-12}


<small>
**Usage:** If Bank staff use this data to create a map- print, web, presentations for an external audience (e.g. external web sites), etc., staff must receive legal clearance by submitting the finished map to the World Bank Cartography Unit.

**Limitations:** To report an error in any of the admin boundary files, please raise a new issue here: https://github.com/worldbank/WB_GAD/issues and it will be considered during the next update cycle.

**Examples:** NA

**Access:** NA
</small>

::: panel-tabset

## R
```{r}
#| echo: false
#| output: asis
if (file.exists("../code/NA")) {
  cat("```r
")
  try(cat(readLines("../code/NA"), sep = "
"))
  cat("```
")
} else {
  cat("No code
")
}
```

## Output
```{r}
#| echo: false
#| results: hold
if (file.exists("../code/NA")) {
  try(source("../code/NA"))
} else {
  print("None")
}
```

:::

**Last updated:** 10/16/25

:::
:::::::

```{=html}
<div class="secondary-links">
  <div class="secondary-links-container">
      <div class="secondary-links-title">
      </div>
      <div class="grid">
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12">
          <ul>
            <li><a href="http://GeoPov/">Geospatial Poverty Solutions Home</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="https://pipmaps.worldbank.org/">Geospatial poverty portal</a></li>
          </ul>
        </div>
        <div class="g-col-lg-4 g-col-md-4 g-col-sm-12 center-left-border">
          <ul>
            <li><a href="mailto:bbrunckhorst@worldbank.org?subject=GeoPov%20data%20and%20methods%20repository" target="_top">Contact us</a></li>
          </ul>
        </div>
      </div>
    </div>
</div>
```


